% resume.tex
% vim:set ft=tex spell:


% ----------------------------------- Doc Config ------------------------------

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}


% -------------------------------------- Macros -------------------------------

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
    \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{-0.5#1}}%
    \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
    #1 &
    #2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}


% ------------------------------------- Content -------------------------------

\begin{document}

\begin{center}
{\LARGE \textbf{::name::}}

::email::\ \ \textbullet
\ \ ::phone::\ \ \textbullet
\ \ ::website::
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{WORK EXPERIENCE}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Senior Consultant}}
        {\textbf{Nov. 2016 -- Jan. 2018}}
    \\
    \headerrow
        {\emph{::company 3 name::}}
        {\emph{::company 3 city::}}
    \begin{itemize*}
        \item Managed five other consultants and was responsible for managing project
        tracking, delegating incoming tasks, running weekly team syncs, and handling
        escalations.
        \item Conducted performance reviews with reports, both recognizing their
        accomplishments and providing them with actionable feedback on areas where
        they could devote additional focus.
        \item Wrote high-level documentation which provided our team and external
        stakeholders with a general understanding of how various internal systems
        functioned and impacted their processes.
        \item Created custom spreadsheet formulas to calculate support ticket metrics
        with over 60\% higher accuracy than previous methods, giving better insight
        into how team resources were being utilized.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Consultant}}
        {\textbf{Oct. 2015 -- Nov. 2016}}
    \\
    \headerrow
        {\emph{::company 3 name::}}
        {\emph{::company 3 city::}}
    \begin{itemize*}
        \item Streamlined the process for creating custom access controls for tools
        on the internal network and applied to over 250 tools, allowing broad network
        access to be revoked for over 60\% of vendor users in our organization.
        \item Developed rules and data feeds for the client’s access monitoring
        system, which detected 300+ new anomalies in 6 months with over 95\%
        accuracy.
        \item Created and maintained SQL tables that provided aggregate sources of
        frequently used data, that were integrated into numerous projects owned by
        both ours and partner teams.
        \item Regularly assisted other teams with projects that would support our
        objectives, leveraging extensive knowledge of internal systems and creative
        problem solving ability.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Analyst}}
        {\textbf{Dec. 2014 -- Oct. 2015}}
    \\
    \headerrow
        {\emph{::company 2 name::}}
        {\emph{::company 2 city::}}
    \begin{itemize*}
        \item Created and maintained automated access management configurations which
        eliminated the need for manually processing requests from over 15k users.
        \item Developed queries and dashboards to provide team leadership with easily
        digestible data on progress in limiting sensitive access held by vendor users
        within the organization.
        \item Wrote and maintained extensive documentation on operational processes
        which was a primary resource in training seven new team members.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Business Operations Specialist}}
        {\textbf{May 2013 -- May 2014}}
    \\
    \headerrow
        {\emph{::company 1 name::}}
        {\emph{::company 1 city::}}
    \begin{itemize*}
        \item Managed relationship with our distributor, ensuring that they were
        meeting SLA and quickly resolving issues that negatively impacted fulfillment
        times.
        \item Collected and analyzed data to identify internal processes that needed
        to be streamlined and improved.
        \item Personally managed order fulfillment, number porting services, and
        billing for 500+ beta testers. Also monitored beta tester accounts to
        identify indications of fraud or abuse of the system
    \end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{EDUCATION}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Bachelor of Science, Political Science}}
        {\textbf{Graduated May 2013}}
    \\
    \headerrow
        {\emph{::university name::}}
        {\emph{::university city::}}
    \begin{itemize*}
        \item \textbf{Coursework:} Calculus 1-3, Differential Equations, Linear
        Algebra, Physics 1-2, Circuits 1, Mechanics
    \end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{TECHNICAL SKILLS}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
SQL\ \ \textbullet
\ \ Python\ \ \textbullet
\ \ JavaScript\ \ \textbullet
\ \ Bash\ \ \textbullet
\ \ Unit Testing\ \ \textbullet
\ \ Process Scripting/Automation

Process Documentation\ \ \textbullet
\ \ Data Analysis/Reporting\ \ \textbullet
\ \ Troubleshooting\ \ \textbullet
\ \ MS Office/gSuite
\end{description*}
\end{indentsection}

\end{document}
